### 2020-07-27 draft.Rmd
remove JT test, flesh out Tukey Perm HSD

```{r}
wilcox.test(seed_accounts$totbal, seed_accounts$newtotbal,alternative = "greater", paired=TRUE)

@@

Since we have reason to believe that marketing about savings will be more effective than no marketing, and that marketing plus a SEED account will be more effective than just marketing, we will use an ordered k-sample test. Here we use the Jonckheere-Terpstra test as recommended by Higgins. [@Higgins]

@@

$H_a: \theta_x \leq \theta_y \leq \theta_z$ with at least one strict inequality

@@

```{r k-sample JT test}

seed_balchange = seed_accounts$balchange
marketing_balchange = (treated %>% filter(marketing==1))$balchange
control_balchange = (treated %>% filter(control==1, marketing==0))$balchange
x = list(control_balchange, marketing_balchange, seed_balchange)
pJCK(x, method="Monte Carlo")
```

@@

@@

a_1 = calculate_critical(sample_q, 0.1)
a_05 = calculate_critical(sample_q, 0.05)
crit_message = sprintf("critical values of significance levels 0.1 and 0.05 are %s and %s respectively", a_1, a_05)
print(crit_message)

@@

for (row in names(treat_list)){
  for(col in names(treat_list)){
    m[row,col] = mw_stat(treat_list[[row]], treat_list[[col]])
  }
}
print("pairwise statistics greater than or equal to the 0.05 critical value")
print(m >= a_05)
```

@@

A p-value of 0.0001 for the Jonckheere-Terpstra test means that we reject the null hypothesis in favor of the alternate. We conclude that there is a difference in savings between the three groups.

A p-value of 0 for the Tukey HSD permutation test shows that the SEED account is awesome. The matrix shows that the SEED accounts had better savings than the control group and the marketing groups. No other differences were significant.

>>>>

```{r wilcox paired test}
wilcox.test(seed_accounts$totbal, seed_accounts$newtotbal,alternative = "greater", paired=TRUE)
```

@@

We will use the Tukey Permutation HSD Test to conduct a multiple comparison test of these groups. The test statistic will be calculated by taking the maximum absolute value of the Mann-Whitney statistic for each pairwise comparison of the three groups. The p-value will be calculated with a re-sampling approach. We will shuffle the data between groups and recalculate the test statistic 10,000 times. The estimated p-value will be the percentage of test statistics greater than or equal to the observed.

@@

$H_a$

To control for type one error we will use Bonferroni's adjustment for the paired test. Giving an adjusted alpha of $\alpha' = \frac{2\alpha}{k(k-1)} = `r 2 * 0.05 / (k * (k - 1))`$[@Higgins]

@@

@@

seed_balchange = seed_accounts$balchange
marketing_balchange = (treated %>% filter(marketing==1))$balchange
control_balchange = (treated %>% filter(control==1, marketing==0))$balchange

@@

alpha = 0.05
adjusted_alpha = 2*alpha/ (k*(k-1))
print(sprintf("Alpha of %s leads to an adjusted alpha of %s", alpha, adjusted_alpha))

crit_alpha = calculate_critical(sample_q, alpha)
crit_adj = calculate_critical(sample_q, adjusted_alpha)
crit_message = sprintf("critical values of significance levels %s and %s are %s and %s respectively", alpha, adjusted_alpha, crit_alpha, crit_adj)
print(crit_message)

@@

for (row in names(treat_list)){
  for(col in names(treat_list)){
    m[row,col] = mw_stat(treat_list[[row]], treat_list[[col]])
  }
}
print("pairwise statistics greater than or equal to the adjusted alpha critical value")
print(m >= crit_adj)
```

@@

A p-value of 0 for the Tukey HSD permutation test leads us to reject the null hypothesis in favor of the alternative. We conclude that there is a difference in savings between at least two of the groups.

The matrix shows that the SEED accounts had better savings than the control group and the marketing groups. No other differences were significant. This allows us to conclude that the SEED accounts had better savings than the other two groups.
